Translation of B Implementations to the LLVM: Control and Modularity

### 2013-08-28 translation.tex
Added an B implementation example with boolean formulas and operators (and, or, not). Added LLVM scaffolding to instantiate implementation and call its operations. Created a Python data structure representing the abstract syntax tree of that B implementation. Updated the Python module with utility functions to build such data structure. Renamed the scaffolding files so that they better match the corresponding example. Implemented translation of boolean operators. Updated the coverage of the B implementation constructs in the documentation of the translation definition.

\begin{center}
\newcommand{\no}[0]{--}
\newcommand{\yes}[0]{$\circ$}
\begin{tabular}{|l|c|c|c|c|}
\hline
Example nº & 01 & 02 & 03 & 04\\
\hline
variables & \yes & \yes & \yes & \yes \\
constants & \no & \yes & \no & \no \\
op. input & \yes & \no & \yes & \no \\
op. output & \yes & \no & \yes & \no \\
\hline
\multicolumn{5}{|c|}{instructions} \\
\hline
block & \yes & \no & \yes & \yes\\
local var & \no & \no & \yes & \yes \\
identity & \no & \no & \yes & \no \\
becomes equal & \yes & \yes & \yes & \yes \\
operation call & \no & \no & \no & \no \\
condition & \yes & \no & \no & \no \\
case & \no & \no & \no & \no \\
assertion & \no & \no & \no & \no\\
sequence & \yes & \yes & \yes & \yes \\
while & \no & \no & \no & \yes \\
\hline
\multicolumn{5}{|c|}{expressions} \\
\hline
int lit & \yes & \yes & \yes & \yes \\
bool lit & \yes & \yes & \no & \yes \\
vars & \yes & \yes & \yes & \yes \\
loc. vars & \no & \no & \yes & \yes \\
const & \no & \yes & \no & \no \\ 
succ & \no & \yes & \no & \yes \\
pred & \no & \yes & \no & \yes \\
+ & \yes & \no & \no & \yes \\
- & \yes & \no & \no & \no\\
\hline
\multicolumn{5}{|c|}{formulas} \\
\hline
and & \no & \no & \no & \no \\
or & \no & \no & \no & \no \\
not & \no & \no & \no & \no \\
$<$ & \yes & \yes & \no & \no\\
\hline
\end{tabular}
\end{center}

@@

>>>>

@@

\newpage
\appendix

\section{Test summary}

For each test file, indicates the B0 constructs found in the implementation.
\begin{center}
\newcommand{\no}[0]{--}
\newcommand{\yes}[0]{$\circ$}
\begin{tabular}{|l|c|c|c|c|c|}
\hline
Example nº & 01 & 02 & 03 & 04 & 05\\
\hline
variables & \yes & \yes & \yes & \yes & \yes\\
constants & \no & \yes & \no & \no & \yes\\
op. input & \yes & \no & \yes & \no & \no \\
op. output & \yes & \no & \yes & \no & \no \\
\hline
\multicolumn{6}{|c|}{instructions} \\
\hline
block & \yes & \no & \yes & \yes & \no\\
local var & \no & \no & \yes & \yes & \no \\
identity & \no & \no & \yes & \no & \no \\
becomes equal & \yes & \yes & \yes & \yes & \yes\\
operation call & \no & \no & \no & \no & \no \\
condition & \yes & \no & \no & \no & \yes\\
case & \no & \no & \no & \no & \no \\
assertion & \no & \no & \no & \no & \no \\
sequence & \yes & \yes & \yes & \yes & \no \\
while & \no & \no & \no & \yes & \no \\
\hline
\multicolumn{6}{|c|}{expressions} \\
\hline
int lit & \yes & \yes & \yes & \yes & \yes\\
bool lit & \yes & \yes & \no & \yes & \yes\\
vars & \yes & \yes & \yes & \yes & \no \\
loc. vars & \no & \no & \yes & \yes & \no \\
const & \no & \yes & \no & \no & \yes\\ 
succ & \no & \yes & \no & \yes & \yes\\
pred & \no & \yes & \no & \yes & \yes\\
+ & \yes & \no & \no & \yes & \no \\
- & \yes & \no & \no & \no & \no\\
\hline
\multicolumn{6}{|c|}{formulas} \\
\hline
and & \no & \no & \no & \no & \yes\\
or & \no & \no & \no & \no & \yes\\
not & \no & \no & \no & \no & \yes\\
$<$ & \yes & \yes & \no & \no & \no\\
$>$ & \no & \no & \no & \no & \yes \\
\hline
\end{tabular}
\end{center}
